Material Methods

### 2020-04-18 doc/MatMeth.Rmd
more edits to methods

chrm chrteriztions -- SC length (chromatin compaction), foci position(raw and normalized), and interfocal distance, 
these traits were fit into the main models (as mentioned above) ... t.tests were used to test between sexes and groups

**CO Interferecne**  -- Our primary mode of examining interference is to compared the interfocal disatnces (IFDs) (raw and normalized by SC length.)  -- Gamma parameter v has historically been used to charaecterize interference and was calculated using <x function>.

@@

**IFD, Interference**

In order to examine interference, Interfocal distance was measured from the single bivalent data sets.
- This metric is closer to measures of interference from linkage maps which are also removed from physical scales in that they measure frequencies of crossovers. Crossover interference is stronger in male specific linkage maps compared to female maps in a variety of species (ref).  **IFD^norm^**

@@

Using the single bivalent dataset, the within cell distribution of bivalent SC lengths from cells with at least 17 isolated chromosome measures. The longest and shortest 4 to 5 chromosomes within each cell were identified by qualqulating the fourth and second quartille. (these comprised the short and long bivalent datasets).

>>>>

**other traits** were also charaecterized -- SC length (a marker for chromatin compaction), foci position (raw and normalized), and interfocal distance a marker for interference, these traits were fit into the main models (as mentioned above).
In addition to fiting the mouse means into the models discribed above, t.tests were used to test the means between sexes and groups.

**IFD, Interference** In order to examine interference, Interfocal distance was measured from the single bivalent data sets. - This metric is closer to measures of interference from linkage maps which are also removed from physical scales in that they measure frequencies of crossovers. Crossover interference is stronger in male specific linkage maps compared to female maps in a variety of species (ref).  **IFD^norm^**

@@

@@

Using the single bivalent dataset, the within cell distribution of bivalent SC lengths from cells with at least 17 isolated chromosome measures. The longest and shortest 4 to 5 chromosomes within each cell were identified by calculating the fourth and second quartille.
